Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
ok

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "default"
    colortheme: "dolphin"
---

@@

@@

![](parsing.png) ![](iceberg.png)

@@

```{r, message=FALSE, warning=FALSE,echo=TRUE}
polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
polish_place("Sur l'imprimea londres")
```

@@

```{r, fig.width=10, fig.height=7, message=FALSE, warning=FALSE}
library(bibliographica)
titlecount_timeline(subset(df0, catalog == "Fennica"), 
          "publisher", nmin = 500, mode = "n")$plot
```

@@

```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5, eval=FALSE}
library(dplyr)
library(ggmap)
library(ggplot2)
library(gisfin)
source("funcs.R")
theme_set(get_theme_map())
mapdata <- filter(df0,
          (catalog == "Kungliga" &
	      publication_place %in% c("Stockholm", "Uppsala",
	                         "Greifswald", "Lund", "Tartu"))|
	  (catalog == "Fennica" &
	      publication_place == "Turku")) %>%
      group_by(publication_decade, publication_place,
	       latitude, longitude) %>%
      summarise(n = n())

@@

### Explaining the 1760-1770 publishing peak in Sweden

Pamphleteering plays a crucial role during abolished censorship in Sweden.

@@

theme_set(theme_bw(20))
p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
     xlab("Publication year") +
     ylab("Title count frequency (%)") +
     #ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
     ggtitle(catalogue) +
     guides(fill = guide_legend(reverse = TRUE, title = "")) +
     scale_fill_brewer(palette="Paired")
pics[[catalogue]] <- p
library(dplyr)
library(magrittr)
}
library(gridExtra)
grid.arrange(p[[1]], p[[2]], nrow = 2)
```

@@

```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=15}
pics <- list()
theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")

@@

  for (myplace in myplaces) {
    p <- ggplot(subset(dff, publication_place == myplace), aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
      xlab("Publication year") +
      ylab("Title count frequency (%)") +
      #ggtitle(paste("Languages (", myplace, "/", catalogue, ")", sep = "")) +
      ggtitle(paste(myplace, "/", catalogue)) +
      scale_fill_brewer(palette="Paired")
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
       geom_line() + geom_point() +
       ggtitle("Number of subject topics")

@@

- Form of literature denoting the advancement of reading in Finland in the nineteenth century. It has been unclear when does it show up as a relevant category.

```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
  print(p)
```

@@

```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
theme_set(theme_bw(20))
for (catalogue in c("Fennica", "Kungliga")) {
  df <- filter(df0, catalog == catalogue) %>%
        filter(publication_year >= 1640 & publication_year <= 1828)
  top.authors <- names(bibliographica::top(df, field = "author", n = 10))
  dfs <- df %>% filter(author %in% top.authors) %>%
         group_by(author, publication_decade) %>%
         tally() %>%
         arrange(publication_decade)
  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +
       xlab("Publication Decade") +
       ylab("Title Count") +
       scale_fill_grey() +
       guides(fill = guide_legend("Author")) +
       ggtitle(paste("Title count top authors\n", catalogue)) +
       xlim(c(1640, 1828))
  print(p)
}
```

```{r authors24, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
theme_set(theme_bw(20))
for (catalogue in c("Fennica", "Kungliga")) {
  df <- filter(df0, catalog == catalogue) %>%filter(gatherings == "8vo")%>%
        filter(publication_year >= 1640 & publication_year <= 1828)
  top.authors <- names(bibliographica::top(df, field = "author", n = 10))
  dfs <- df %>% filter(author %in% top.authors) %>%
         group_by(author, publication_decade) %>%
         tally() %>%
         arrange(publication_decade)
  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +
       xlab("Publication Decade") +
       ylab("Title Count") +
       scale_fill_grey() +
       guides(fill = guide_legend("Author")) +
       ggtitle(paste("Title count top authors\n", catalogue)) +
       xlim(c(1640, 1828))
  print(p)
}
```

@@

Source code for these slides:
- https://github.com/rOpenGov/fennica/blob/master/inst/examples/20160715-slides-Krakow.Rmd

>>>>

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "Montpellier"
    colortheme: "default"
    fonttheme: "structuresmallcapsserif"
---

@@

sivu 12. Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata mitkä vuodet highlightataan. Tällaisena ei vielä toimi. Onhan katalogi oikein?

@@

\begin{columns}
\begin{column}{0.5\textwidth}
     \includegraphics[width=1\textwidth]{parsing.png}
\end{column}
\begin{column}{0.5\textwidth}  %%<--- here
    \begin{center}
     \includegraphics[width=1\textwidth]{iceberg.png}
     \end{center}
\end{column}
\end{columns}

![](ecosystemflowchart.png)

@@

```{r, message=FALSE, warning=FALSE,echo=TRUE}
polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
```

@@

```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
titlecount_timeline(subset(df0, catalog == "Fennica"), 
          "publisher", nmin = 500, mode = "n")$plot
```

@@

```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5, eval=TRUE}
library(dplyr)
library(ggmap)
library(ggplot2)
library(gisfin)
source("funcs.R")
theme_set(get_theme_map())
mapdata <- filter(df0,
          (catalog == "Kungliga" &
	      publication_place %in% c("Stockholm", "Uppsala",
	                         "Greifswald", "Lund", "Tartu"))|
	  (catalog == "Fennica" &
	      publication_place == "Turku")) %>%
      group_by(publication_decade, publication_place,
	       latitude, longitude) %>%
      summarise(n = n())

@@

### Swedish 1760-1770 publishing peak

Pamphleteering plays a crucial role during abolished censorship

@@

theme_set(theme_bw(20))
p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
     xlab("Publication year") +
     ylab("Title count frequency (%)") +
     #ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
     ggtitle(catalogue) +
     guides(fill = guide_legend(reverse = TRUE, title = "")) +
     scale_fill_brewer(palette="Paired")
pics[[catalogue]] <- p
}
library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], nrow = 2)
```

@@

```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}
pics <- list()
theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")

@@

  for (myplace in myplaces) {
    p <- ggplot(subset(dff, publication_place == myplace), aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
      xlab("Publication year") +
      ylab("Title count frequency (%)") +
      #ggtitle(paste("Languages (", myplace, "/", catalogue, ")", sep = "")) +
      ggtitle(paste(myplace, "/", catalogue)) +
      scale_fill_brewer(palette="Paired") + 
      guides(fill = guide_legend(reverse = TRUE, title = ""))
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
       geom_line() + geom_point()

@@

Form of literature denoting the advancement of reading in Finland in the nineteenth century. It has been unclear when does it show up as a relevant category.

```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(catalogue) 
       #ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
  print(p)
```

@@

```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="160px", fig.show="hold"}
theme_set(theme_bw(20))
for (catalogue in c("Fennica", "Kungliga")) {
  df <- filter(df0, catalog == catalogue) %>%
        filter(publication_year >= 1640 & publication_year <= 1828)
  top.authors <- names(bibliographica::top(df, field = "author", n = 10))
  dfs <- df %>% filter(author %in% top.authors) %>%
         group_by(author, publication_decade) %>%
         tally() %>%
         arrange(publication_decade)
  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +
       xlab("Publication Decade") +
       ylab("Title Count") +
       scale_fill_grey() +
       guides(fill = guide_legend("Author")) +
       ggtitle(paste("Title count top authors\n", catalogue)) +
       xlim(c(1640, 1828))
  print(p)
}
```

@@

Source code of these slides:
- https://github.com/rOpenGov/fennica/blob/master/inst/examples/20160715-slides-Krakow.Rmd
